Constraining the Interiors of Asteroids Through Close Encounters

### 2022-08-26 paper/arxiv/main.tex
Updated mnras version

%% Julien asks that I use mean and max values in each plot instead of chisq.

@@

  \includegraphics[width=0.49\linewidth]{figs/side-by-side-u}
  \caption{Cross-sectional slices of the extracted distribution (\textit{left}) and true distribution (\textit{right}) of the asymmetric reference asteroid. The density distribution was created via the lumpy model. Uncertainty in the distribution is shown below. The extracted distribution is nearly identical to the true distribution and is statistically consistent with the truth.}
  \label{fig:den-side-by-side}
\end{figure}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core. From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplemental Data. The lumpy model successfully extracts the core.}
  \label{fig:den-move}
\end{figure*}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core. From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplemental Data. The resulting density distribution is consistent with the density moments but does not represent the true distribution due to degeneracy.}
  \label{fig:den-sph}
\end{figure*}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores. From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplemental Data. The additional lump greatly increases uncertainty, but the resulting distribution is close to accurate.}
  \label{fig:den-double}
\end{figure*}

@@

All the code used in this paper --- namely, AIME --- are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/aime}}. The data showcased here was generated from that code. Please contact JTD with questions.

@@

\input{appendices}

>>>>

@@

  \includegraphics[width=0.49\linewidth]{figs/side-by-side-u}
  \caption{Cross-sectional slices of the extracted distribution (\textit{left}) and true distribution (\textit{right}) of the asymmetric reference asteroid. The density distribution was created via the lumpy model. Uncertainty in the distribution is shown below. The extracted distribution is nearly identical to the true distribution and is statistically consistent with the truth. These figures are available in animated form in the Supplementary Material.}
  \label{fig:den-side-by-side}
\end{figure}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core. From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplementary Material. The lumpy model successfully extracts the core.}
  \label{fig:den-move}
\end{figure*}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core. From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplementary Material. The resulting density distribution is consistent with the density moments but does not represent the true distribution due to degeneracy.}
  \label{fig:den-sph}
\end{figure*}

@@

  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores. From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted. These figures are available in animated form in the Supplementary Material. The additional lump greatly increases uncertainty, but the resulting distribution is close to accurate.}
  \label{fig:den-double}
\end{figure*}

@@

All the code used in this paper --- namely, AIME --- are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/AIME}}. The data showcased here was generated from that code. Please contact JTD with questions.

@@

% \input{appendices}
